Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-09-03 data/result/Article/Latex/Article.tex
Revisão da RQ2

On regard on I$_{C}$, SH contributed with more vertices to the reference Pareto front than the average front produced by each cycle of NSGAII in 4 out of 6 instances. For the remaining instances, results slightly favor NSGAII, but without statistical significance in comparison with SH. On average, SH contributed with 5.2 solutions to the reference front, while NSGAII contributed with 2.4 solutions. Each remaining OMS contributed with a single solution to the front (zero overtime). On regard of I$_{HV}$, NSGAII produced the best results except for the largest instance (PARM), on which it was significantly outperformed by SH. Finally, on regard of I$_{GD}$ NSGAII outperformed all OMS in 4 out of 6 instances, losing to SH on the OMET and PARM instances (the largest instances). For the latter, all solutions produced by SH were part of the reference front. Thus, we ratify the results presented by Ferrucci et al. \cite{Ferrucci:2013} in the sense that the CPM and margarine OMS are not competitive with optimization results. On the other hand, SH seems competitive and outperforms NSGAII in terms of closeness to the reference front on large instances.

\begin{figure*}
\centering
\includegraphics[width=18cm, height=5cm]{boxplots2.pdf}
\caption{Boxplots for I$_{C}$ (left), I$_{HV}$ (middle) and I$_{GD}$ (right) quality indicators for NSGAII (boxplot), MAR ($\times$), SH ($\ast$), and CPM (+). The few solutions found under the second-half OMS are closer to optimal, though NSGAII produces a more diverse set of solutions.}
\end{figure*}

% Table generated by Excel2LaTeX from sheet 'tabela 2'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicator values for each instance under our approach (NSGAII) and the OMS. Pareto fronts produced under NSGAII present more diversity than those produced under the OMS. Solutions produced under the Second-Half OMS are closer to optimal for the largest instances.}
    \begin{tabular}{p{0.7cm} p{0.7cm} ccc}
    \toprule
    \textbf{Instance} & \textbf{Config} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{4}[2]{*}{ACAD} & NSGAII & \textbf{0.0196 $\pm$ 0.0109} & \textbf{0.4999 $\pm$ 0.0037} & \textbf{0.0033 $\pm$ 0.0012} \\
          & MAR   & 0.0068 & 0.2303 & 0.1782 \\
          & SH    & 0.0103 & 0.3589 & 0.0457 \\
          & CPM   & 0.0068 &    n/a &    n/a \\\hline
    \multirow{4}[2]{*}{WMET} & NSGAII & \textbf{0.0196 $\pm$ 0.0113} & \textbf{0.4859 $\pm$ 0.0029} & \textbf{0.0023 $\pm$ 0.0003} \\
          & MAR   & 0.0068 & 0.2544 & 0.2394 \\
          & SH    & 0.0103 & 0.3538 & 0.0390 \\
          & CPM   & 0.0068 & 0.1913 & 0.1508 \\\hline
    \multirow{4}[2]{*}{WAMS} & NSGAII & \textbf{0.0196 $\pm$ 0.0096} & \textbf{0.4808 $\pm$ 0.0027} & \textbf{0.0018 $\pm$ 0.0003} \\
          & MAR   & 0.0069 & 0.2547 & 0.2406 \\
          & SH    & 0.0103 & 0.3547 & 0.0381 \\
          & CPM   & 0.0069 & 0.1718 & 0.1502 \\\hline
    \multirow{4}[2]{*}{PSOA} & NSGAII & \textbf{0.0197 $\pm$ 0.0108} & \textbf{0.3692 $\pm$ 0.0044} & \textbf{0.0047 $\pm$ 0.0016} \\
          & MAR   & 0.0086 & 0.1589 & 0.1738 \\
          & SH    & 0.0086 & 0.2425 & 0.1577 \\
          & CPM   & 0.0086 &    n/a &    n/a \\\hline
    \multirow{4}[2]{*}{OMET} & NSGAII & \textbf{0.0195 $\pm$ 0.0108} & \textbf{0.4394 $\pm$ 0.0038} & \textbf{0.0022 $\pm$ 0.0002} \\
          & MAR   & 0.0100 & 0.2562 & 0.2207 \\
          & SH    & 0.0150 & 0.3579 & 0.0249 \\
          & CPM   & 0.0100 & 0.2109 & 0.1280 \\\hline
    \multirow{4}[2]{*}{PARM} & NSGAII & 0.0187 $\pm$ 0.0173 & \textbf{0.3963 $\pm$ 0.0044} & \textbf{0.0047 $\pm$ 0.0008} \\
          & MAR   & 0.0165 & 0.2308 & 0.1511 \\
          & SH    & \textbf{0.0496} & 0.3579 & 0.0172 \\
          & CPM   & 0.0165 & n/a   & n/a \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

The {\^A12} effect-size was calculated for pair-wise comparisons between NSGAII and each OMS for all quality indicators. Results are presented in Table III, denoting the chances of NSGAII to produce higher I$_C$ and I$_{HV}$ and lower I$_{GD}$ than the related OMS. {\^A}12 is very high and favors NSGAII in almost all instances for I$_{HV}$ and I$_{GD}$ (except PARM for I$_{HV}$, OMET and PARM for I$_{GD}$). It strongly favors NSGAII in terms of $I_C$ if compared to MAR and CPM, except on PARM (a draw on effect-size among both OMS and NSGAII). On the other hand, {\^A}12 tells a different story for I$_{C}$ between NSGAII and SH, clearly favoring SH for almost all instances.

Effect-sizes are in agreement with former results indicating that MAR and CPM are not effective overtime management strategies. Moreover, effect-sizes provide additional evidence on the differences between NSGAII and SH: if there is enough time to run the optimization/simulation process, NSGAII can produce Pareto fronts which present more diversity than those resulting from SH, but the latter can quickly provide a good approximation (limited to a few points) for the reference front. Thus, the industry has good reason for concentrating overtime on the second half of project schedules, but it can improve its practices by combining SH with our proposed approach in order to provide more overtime allocation alternatives for the decision maker.

\vspace{3px}
\noindent
\textbf{RQ3:} To address this question we compared our approach (NSGAII) with a similar formulation without the increased error generation rates caused by working overtime (NSGA$_{NE}$). We aim to observe if ignoring the increase in error generation rates would change a decision-makers' perceptions on which overtime planning alternative should be selected for a project. Table IV presents summary values for the quality indicators calculated over 50 optimization cycles for each algorithm. All values are presented in the mean $\pm$ standard deviation format. Complete box-plots were suppressed due to space limitations. Bold face values are significantly different compared to the other algorithm, as ascertained by Wilcoxon-Mann-Whitney tests at 95\% confidence level.

>>>>

On regard on I$_{C}$, NSGAII outperformed all OMS in 5 out of 6 instances. On average, each NSGAII cycle contributed with 4.7 solutions to the reference front, SH contributed with 3.3 solutions, MAR and CPM added 2.0 solutions each. Solutions generated under CPM concentrated in the parts of the solution space representing few overtime hours, a region not frequently accessed by NSGAII. All OMS added the solution representing zero overtime to the reference front. For the largest instance, SH provided more solutions than the average run of NSGAII. On regard of I$_{HV}$ and I$_{GD}$, NSGAII produced the best results for all instances. SH also provided Pareto fronts with high I$_{HV}$ and low I$_{GD}$ (as shown in the box-plots in Figure I) though not as high/low as NSGAII due to the number of vertices comprising the latter's fronts. Thus, we ratify the results presented by Ferrucci et al. \cite{Ferrucci:2013} in the sense that the CPM and margarine OMS are not competitive with optimization results. On the other hand, SH is a good approximation for NSGAII, particularly for large instances. The good performance shown by SH can be explained by the error propagation/regeneration dynamics: if overtime is concentrated towards the end of the schedule, we suppress the snowball-growth in the number of errors reaching testing activities.

\begin{figure*}
\centering
\includegraphics[width=18cm, height=5cm]{boxplots2.pdf}
\caption{Box-plots for I$_{C}$ (left), I$_{HV}$ (middle) and I$_{GD}$ (right) quality indicators for NSGAII (box-plot), MAR ($\times$), SH ($\ast$), and CPM (+). The few solutions found under the second-half OMS are closer to optimal, though NSGAII produces a more diverse set of solutions.}
\end{figure*}

% Table generated by Excel2LaTeX from sheet 'tabela 2'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicator values for each instance under our approach (NSGAII) and the OMS. Pareto fronts produced under NSGAII present more diversity than those produced under the OMS. Solutions produced under the Second-Half OMS are closer to optimal for the largest instance.}
    \begin{tabular}{p{0.7cm} p{0.7cm} ccc}
    \toprule
    \textbf{Instance} & \textbf{Config} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{4}[2]{*}{ACAD} & NSGAII & \textbf{0.0196 $\pm$ 0.0109} & \textbf{0.4999 $\pm$ 0.0037} & \textbf{0.0033 $\pm$ 0.0012} \\
          & MAR   & 0.0068 & 0.2303 & 0.1782 \\
          & SH    & 0.0103 & 0.3589 & 0.0457 \\
          & CPM   & 0.0068 &    n/a &    n/a \\\hline
    \multirow{4}[2]{*}{WMET} & NSGAII & \textbf{0.0196 $\pm$ 0.0113} & \textbf{0.4859 $\pm$ 0.0029} & \textbf{0.0023 $\pm$ 0.0003} \\
          & MAR   & 0.0068 & 0.2544 & 0.2394 \\
          & SH    & 0.0103 & 0.3538 & 0.0390 \\
          & CPM   & 0.0068 & 0.1913 & 0.1508 \\\hline
    \multirow{4}[2]{*}{WAMS} & NSGAII & \textbf{0.0196 $\pm$ 0.0096} & \textbf{0.4808 $\pm$ 0.0027} & \textbf{0.0018 $\pm$ 0.0003} \\
          & MAR   & 0.0069 & 0.2547 & 0.2406 \\
          & SH    & 0.0103 & 0.3547 & 0.0381 \\
          & CPM   & 0.0069 & 0.1718 & 0.1502 \\\hline
    \multirow{4}[2]{*}{PSOA} & NSGAII & \textbf{0.0197 $\pm$ 0.0108} & \textbf{0.3692 $\pm$ 0.0044} & \textbf{0.0047 $\pm$ 0.0016} \\
          & MAR   & 0.0086 & 0.1589 & 0.1738 \\
          & SH    & 0.0086 & 0.2425 & 0.1577 \\
          & CPM   & 0.0086 &    n/a &    n/a \\\hline
    \multirow{4}[2]{*}{OMET} & NSGAII & \textbf{0.0195 $\pm$ 0.0108} & \textbf{0.4394 $\pm$ 0.0038} & \textbf{0.0022 $\pm$ 0.0002} \\
          & MAR   & 0.0100 & 0.2562 & 0.2207 \\
          & SH    & 0.0150 & 0.3579 & 0.0249 \\
          & CPM   & 0.0100 & 0.2109 & 0.1280 \\\hline
    \multirow{4}[2]{*}{PARM} & NSGAII & 0.0187 $\pm$ 0.0173 & \textbf{0.3963 $\pm$ 0.0044} & \textbf{0.0047 $\pm$ 0.0008} \\
          & MAR   & 0.0165 & 0.2308 & 0.1511 \\
          & SH    & \textbf{0.0496} & 0.3579 & 0.0172 \\
          & CPM   & 0.0165 & n/a   & n/a \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

The {\^A12} standardized effect-size was calculated for pair-wise comparisons between NSGAII and each OMS for all quality indicators. Results are presented in Table III, denoting the chances of NSGAII to produce higher I$_C$ and I$_{HV}$ and lower I$_{GD}$ than the related OMS. {\^A}12 is very high and favors NSGAII for all instances for I$_{HV}$ and I$_{GD}$. It also strongly favors NSGAII in terms of $I_C$ if compared to MAR and CPM, except on PARM (a draw on effect-size among both OMS and NSGAII). However, {\^A}12 tells a different story for I$_{C}$ between NSGAII and SH, clearly favoring SH for the largest instance. Effect-sizes are in agreement with former results indicating that MAR and CPM are not effective OMS. They also provide additional evidence on the differences between NSGAII and SH: if there is enough time to run the optimization process, NSGAII can produce Pareto fronts which present more diversity and are closer to optimal than those resulting from SH, but the latter can quickly provide an approximation for the reference front. Thus, the industry has good reasons for concentrating overtime on the second half of project schedules, but it can improve its practices by combining SH with our approach in order to provide more overtime allocation alternatives for the decision maker.

\vspace{3px}
\noindent
\textbf{RQ3:} To address this question we compared our approach (NSGAII) with a similar formulation without the increased error generation rates caused by working overtime (NSGA$_{NE}$). We aim to observe if ignoring the increase in error generation rates would change a decision-makers' perceptions on which overtime planning alternative should be selected for a project. Table IV presents summary values for the quality indicators calculated over 50 optimization cycles for each algorithm. All values are presented in the mean $\pm$ standard deviation format. Complete box-plots were suppressed due to space limitations. Bold face values are significantly different compared to the other algorithm, as ascertained by Wilcoxon-Mann-Whitney tests at 95\% significance level.
